Robotic Cart System

### 2021-09-14 paperIEEE-ROSE2021-BrBeAlShMi.tex
Conference paper version Sep 13, 2021
Update paperIEEE-ROSE2021-BrBeAlShMi.tex

A robotic cart is an invention designed to aid users in a number of important
indoor and outdoor tasks. There are robotic systems currently available in the
market that perform these tasks in a variety of ways. For example, in a grocery
store, a customer may require the need of more than one cart but cannot push or
pull two carts simultaneously. One major drawback, however, is that people with
disabilities cannot push one cart let alone have a second cart to carry more
items. Moreover, robots used for this purpose are costlier than they are worth.
Here we propose a robotic cart that would primarily leverage the emerging radio
frequency identification (RFID) technology, where analog radio frequency signals
are utilized to identify the remote (a customer in a grocery store, for
instance) and the robotic cart be able to track and follow the remote. The
implementation of such a fully functional robotic cart will outreach the scope
of the current work but is the overall goal of this ongoing project.

Abundant research carried out in the field of mobile robotics shows various ways to develop
robotic carts that will help consumers in carrying groceries through stores.
See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example. The operating principle of several robotic carts available in the market focuses on a few different methods of having a
robotic cart interface with the customer and follow them through the store. One such method that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmission technology is shown in Fig.~\ref{fig:CompaRob}~\cite{Sales2016-CompaRob}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob robot~\cite{Sales2016-CompaRob}.}
   \label{fig:CompaRob}
 \end{figure}
% 
 Authors in~\cite{islam_lam_fukuda_kobayashi_kuno_2019} have developed a shopping
 support robot that employs a GRU (Gated Recurrent Unit) network to detect
 shopping habits of customers. The robot is also equipped with a LiDAR (Light
 Detection and Ranging) sensor and camera for detecting and building map of the
 customer's position using a two-dimensional skeleton and follow the customer
 through the store. The robot developed using such an algorithm is  shown in Fig.~\ref{fig:ShoppingSup}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping Support Robot}
   \label{fig:ShoppingSup}
\end{figure}
%
Fig.~\ref{fig:SmartCart} shows a smart cart robot that has been developed by the authors in~\cite{Rawashdeh2017-Person}. The authors utilized an Arduino MEGA 2560, six
ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android
Studio IDE device, and Bluetooth for detecting a customer and following them
through the store. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.45\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}
%
The operating principle of the proposed prototype of a smart robotic cart relies mainly on the radio frequency identification technology. For that, RF modules, XBee S2C RF radios, are primarily utilized to identify and communicate between the robotic cart and the remote (customer in a store, for example). XBee S2C RF radios are inexpensive and easily configurable. An RF module is configured as a remote target device that is carried
by the user/customer. The robot will be able to track this remote instead of using line
of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF
radios, the robot is equipped with a parabolic reflector, which improves radio
reception at various distances and angles,~\textit{i.e.,} angle of arrivals of
RF signals from the remote, based on research done previously in this type of
robot localization and mapping~\cite{Miah2018-Intelligent,Li2013ANA}. The approach using signal strengths of RF signals also requires an understanding
of multipath interference which is common in RF based wireless positioning
sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using
course estimation calculations such as the received signal strength indicator (RSSI)
 together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath
interference.

@@

\section{System Architecture}
\label{sec:systemArchitecture}
The proposed smart robotic cart is a wheeled mobile robot that sends and
receives radio signals to follow the remote target (customer in a store, for
example) which acts as a beacon. The high-level system block diagram of the
proposed robotic cart (prototype) is shown in Fig.~\ref{fig:sys_block_diag}. %
% 
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.2]{figs/systemBlockDiagram.pdf}
  \caption{System level block diagram detailing inputs and outputs to the
    robotic cart system.}
	\label{fig:sys_block_diag}
\end{figure}
% 
There are three inputs to the proposed cart system. The robotic cart is supplied
with power through a battery that is mounted in the chassis of the robotic cart.
There will be an on/off switch to allow the cart to be powered down when not in
use. This will save the battery from being drained by other electronic
components of the robot. The motion of the robotic cart is dependent on the
motion of the remote. The main output of the system is the position trajectory
of the robotic cart in its environment. When the user/customer moves with the
remote target, the robotic cart is designed to follow the user.

As can be seen, two subsystems (mobile cart and remote) of the proposed robotic cart communicate with one another by relaying radio messages between them. Fig.~\ref{fig:remote_block_diag} shows the block diagram of the remote. %
%
\begin{figure}[htbp]
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \caption{}
    \label{fig:remote_block_diag}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \caption{}
    \label{fig:mobile_block_diag}
  \end{subfigure}
  \caption{Block diagrams showing inputs and outputs of:~\subref{fig:remote_block_diag} remote and~\subref{fig:mobile_block_diag}~mobile cart of the proposed smart robotic cart.}
  \label{fig:blockDiagramRemoteMobileCart}
\end{figure}
%
It requires an RF module, XBee, attached to $7.4~[\si{\volt}]$ Li-Po battery
with a voltage regulation circuit since the XBee has a smaller input voltage of
$3.3~[\si{\volt}].$ The two inputs of the remote are the battery power and the
incoming RF messages which are passed through the RF transceiver. The remote
outputs the an RF message back to the mobile cart, which will be discussed
later. The subsystem block diagram of the mobile cart is shown in
Fig.~\ref{fig:mobile_block_diag}. The cart requires a power source, which will
be a $7.4~[\si{\volt}],$ $8000~[\si{\milli\ampere\hour}]$ Li-Po battery since the Li-Po works well with powering the
embedded computer. The power to the subsystem will be toggled
by an on/off switch located on the chassis of the robotic cart. The final input
to the mobile cart subsystem are the incoming RF signals and the wheel velocities for the cart's actuators. These incoming RF
signals are passed to the direction sensitive RF receivers which output the
signals to the dual-direction multiplexer. The dual-direction multiplexer then
takes the four inputs from the direction sensitive RF receivers and passes one
output into the embedded computer. Once the embedded computer gets these signals
it can apply localization and navigation algorithms and pass the necessary actuator commands to the actuators of the robotic cart.

@@

After the robotic cart and the remote were built, several different variants of
the algorithms were tested. There were two main types of variants tested. In one
variant, the stepper motor is locked, preventing the reflector from rotating. In
the other variant, the stepper motor is used to sweep through the angles. The
experiments with the complete prototype of the proposed smart robotic cart shown
in Fig.~\ref{fig:finishedPrototypes} were conducted on a hallway, a laboratory
floor, and the ground floor of the Business and Engineering Convergence Center
of Bradley University. %
%
\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/71.jpeg} 
    \caption{}
    \label{fig:71}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/141.jpeg} 
    \caption{}
    \label{fig:141}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
   \centering
   \includegraphics[width=\textwidth]{videos/frames/211.jpeg} 
   \caption{}
   \label{fig:211}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/351.jpeg} 
    \caption{}
    \label{fig:351}
  \end{subfigure}
  \\
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/491.jpeg} 
    \caption{}
    \label{fig:491}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/561.jpeg} 
    \caption{}
    \label{fig:561}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/631.jpeg} 
    \caption{}
    \label{fig:631}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.24\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/701.jpeg} 
    \caption{}
    \label{fig:701}
  \end{subfigure}
  %
  \caption{Experiment results demonstrating the performance of the proposed smart robotic cart in following the remote.}
  \label{fig:experResultsImages}
\end{figure}
%
Fig.~\ref{fig:experResultsImages} summarizes the performance of the proposed smart robotic cart. A person holding the remote shown in Fig.~\ref{fig:remotePrototype} follows a random trajectory. As can be seen, the mobile cart shown in Fig.~\ref{fig:overallPrototype} is able to follow the remote regardless of the navigation environment of both of the remote and the mobile cart.

>>>>

A robotic cart is an invention designed to aid users in a number of important
indoor and outdoor tasks. There are robotic systems currently available in the
market that perform these tasks in a variety of ways. For example, in a grocery
store, a customer may require the need of more than one cart but cannot push or
pull two carts simultaneously. One major drawback, however, is that people with
disabilities cannot push one cart let alone have a second cart to carry more
items. Moreover, robots used for this purpose can range in cost from \$5,000 to \$10,000 per unit. 
Here we propose a robotic cart that would primarily leverage the emerging radio
frequency identification (RFID) technology, where analog radio frequency signals
are utilized to identify the remote (a customer in a grocery store, for
instance) and the robotic cart be able to track and follow the remote. The
implementation of such a fully functional robotic cart will outreach the scope
of the current work but is the overall goal of this ongoing project.

Abundant research carried out in the field of mobile robotics shows various ways to develop
robotic carts that will help consumers in carrying groceries through stores.
See~\cite{Rawashdeh2017-Person,islam_lam_fukuda_kobayashi_kuno_2019,Sales2016-CompaRob}, for example. The operating principle of several robotic carts available in the market focuses on a few different methods of having a
robotic cart interface with the customer and follow them through the store. One such method that has been utilized to make a mobile cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmission technology is shown in Fig.~\ref{fig:CompaRob}~\cite{Sales2016-CompaRob}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
   \caption{CompaRob robot~\cite{Sales2016-CompaRob}.}
   \label{fig:CompaRob}
 \end{figure}
% 
 Authors in~\cite{islam_lam_fukuda_kobayashi_kuno_2019} have developed a shopping
 support robot that employs a GRU (Gated Recurrent Unit) network to detect
 shopping habits of customers. The robot is also equipped with a LiDAR (Light
 Detection and Ranging) sensor and camera for detecting and building map of the
 customer's position using a two-dimensional skeleton and follow the customer
 through the store. The robot developed using such an algorithm is  shown in Fig.~\ref{fig:ShoppingSup}. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.35\textwidth]{figs/img/ShoppingSuportRobot}
   \caption{Shopping support robot.}
   \label{fig:ShoppingSup}
\end{figure}
%
Fig.~\ref{fig:SmartCart} shows a smart cart robot that has been developed by the authors in~\cite{Rawashdeh2017-Person}. The authors utilized an Arduino MEGA 2560, six
ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android
Studio IDE device, and Bluetooth for detecting a customer and following them
through the store. %
%
\begin{figure}[htpb]
   \centering
   \includegraphics[width=0.40\textwidth]{figs/img/SmartCart}
   \caption{Smart Cart Robot}
   \label{fig:SmartCart}
\end{figure}
%
The operating principle of the proposed prototype of a smart robotic cart relies mainly on the radio frequency identification technology. For that, RF modules, XBee S2C RF radios, are primarily utilized to identify and communicate between the robotic cart and the remote (customer in a store, for example). XBee S2C RF radios are inexpensive and easily configurable. An RF module is configured as a remote target device that is carried
by the user/customer. The robot will be able to track this remote instead of using line
of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF
radios, the robot is equipped with a parabolic reflector, which improves radio
reception at various distances and angles,~\textit{i.e.,} angle of arrivals of
RF signals from the remote, based on research done previously in this type of
robot localization and mapping~\cite{Miah2018-Intelligent,Li2013ANA}. The approach using signal strengths of RF signals also requires an understanding
of multipath interference which is common in RF based wireless positioning
sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using
course estimation calculations such as the received signal strength indicator (RSSI)
 together with the time difference of arrival (TDoA) is key to compensate for the effect of multipath
interference.

@@

\section{System Architecture}
\label{sec:systemArchitecture}
The proposed smart robotic cart is a wheeled mobile robot that sends and
receives radio signals to follow the remote target (customer in a store, for
example) which acts as a beacon. The high-level system block diagram of the
proposed robotic cart (prototype) is shown in Fig.~\ref{fig:sys_block_diag}. %
% 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{figs/systemBlockDiagram.pdf}
  \caption{System level block diagram detailing inputs and outputs to the
    robotic cart system.}
	\label{fig:sys_block_diag}
\end{figure}
% 
There are three inputs to the proposed cart system. The robotic cart is supplied
with power through a battery that is mounted in the chassis of the robotic cart.
There will be an on/off switch to allow the cart to be powered down when not in
use. This will save the battery from being drained by other electronic
components of the robot. The motion of the robotic cart is dependent on the
motion of the remote. The main output of the system is the position trajectory
of the robotic cart in its environment. When the user/customer moves with the
remote target, the robotic cart is designed to follow the user.

As can be seen, two subsystems (mobile cart and remote) of the proposed robotic cart communicate with one another by relaying radio messages between them. Fig.~\ref{fig:remote_block_diag} shows the block diagram of the remote. %
%
\begin{figure}[htbp]
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/remoteBlockDiagram.pdf}
    \caption{}
    \label{fig:remote_block_diag}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \centering
    \includegraphics[width=\textwidth]{figs/mobileCartBlockDiagram.pdf}
    \caption{}
    \label{fig:mobile_block_diag}
  \end{subfigure}
  \caption{Block diagrams showing inputs and outputs of:~\subref{fig:remote_block_diag} remote and~\subref{fig:mobile_block_diag}~mobile cart of the proposed smart robotic cart.}
  \label{fig:blockDiagramRemoteMobileCart}
\end{figure}
%
It requires an RF module, XBee, attached to $7.4~[\si{\volt}]$ Li-Po battery
with a voltage regulation circuit since the XBee has a smaller input voltage of
$3.3~[\si{\volt}].$ The two inputs of the remote are the battery power and the
incoming RF messages which are passed through the RF transceiver. The remote
outputs the RF message back to the mobile cart, which will be discussed
later. The subsystem block diagram of the mobile cart is shown in
Fig.~\ref{fig:mobile_block_diag}. The cart requires a power source, which will
be a $7.4~[\si{\volt}],$ $8000~[\si{\milli\ampere\hour}]$ Li-Po battery since the Li-Po works well with powering the
embedded computer. The power to the subsystem will be toggled
by an on/off switch located on the chassis of the robotic cart. The final input
to the mobile cart subsystem are the incoming RF signals and the wheel velocities for the cart's actuators. These incoming RF
signals are passed to the direction sensitive RF receivers which output the
signals to the dual-direction multiplexer. The dual-direction multiplexer then
takes the four inputs from the direction sensitive RF receivers and passes one
output into the embedded computer. Once the embedded computer gets these signals
it can apply localization and navigation algorithms and pass the necessary actuator commands to the actuators of the robotic cart.

@@

After the robotic cart and the remote were built, several different variants of
the algorithms were tested. There were two main types of variants tested. In one
variant, the stepper motor is locked, preventing the reflector from rotating. In
the other variant, the stepper motor is used to sweep through the angles. The
experiments with the complete prototype of the proposed smart robotic cart shown
in Fig.~\ref{fig:finishedPrototypes} were conducted on a hallway, a laboratory
floor, and the ground floor of the Business and Engineering Convergence Center
of Bradley University. %
%
\begin{figure}[htbp]
  \centering
  \begin{subfigure}[b]{0.30\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/71.jpeg} 
    \caption{}
    \label{fig:71}
  \end{subfigure}
  \begin{subfigure}[b]{0.30\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/141.jpeg} 
    \caption{}
    \label{fig:141}
  \end{subfigure}
  \begin{subfigure}[b]{0.30\linewidth}
   \centering
   \includegraphics[width=\textwidth]{videos/frames/211.jpeg} 
   \caption{}
   \label{fig:211}
 \end{subfigure}
 \\
  \begin{subfigure}[b]{0.30\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/351.jpeg} 
    \caption{}
    \label{fig:351}
  \end{subfigure}
  \begin{subfigure}[b]{0.30\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/491.jpeg} 
    \caption{}
    \label{fig:491}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.30\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/561.jpeg} 
    \caption{}
    \label{fig:561}
  \end{subfigure}
  %
  \\
  \begin{subfigure}[b]{0.30\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/631.jpeg} 
    \caption{}
    \label{fig:631}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.30\linewidth}
    \centering
    \includegraphics[width=\textwidth]{videos/frames/701.jpeg} 
    \caption{}
    \label{fig:701}
  \end{subfigure}
  %
  \caption{Experiment results demonstrating the performance of the proposed smart robotic cart in following the remote.}
  \label{fig:experResultsImages}
\end{figure}
%
Fig.~\ref{fig:experResultsImages} summarizes the performance of the proposed smart robotic cart. A person holding the remote shown in Fig.~\ref{fig:remotePrototype} follows a random trajectory. As can be seen, the mobile cart shown in Fig.~\ref{fig:overallPrototype} is able to follow the remote regardless of the navigation environment of both of the remote and the mobile cart.
